\myshort{} to Enable Systematic Evaluation of Testing Techniques

### 2025-03-21 paper/main.tex
comments

\noindent
The script \CodeIn{install\_freefuzz\_docker.sh} build the docker container
that contains the tool FreeFuzz. The script contains the
following instructions:
% \Fix{add brief explanation for what it does}:

\begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
#!/bin/bash
git clone https://github.com/ise-uiuc/FreeFuzz.git
docker build -t freefuzz .
docker run --name freefuzz --gpus all -d freefuzz:latest
docker exec -it freefuzz mongorestore dump/
\end{lstlisting}

\Fix{Please revise}
The command \CodeIn{run-tool} takes the library version as an input, along with the name of the docker container, the name of the library, and the script that contains the commands to run the tool (\CodeIn{run\_freefuzz\_docker.sh}) and it outputs how many bugs that are reproducible with this library version were successfully reproduced by a tool (e.g. FreeFuzz).
Tool execution proceeds as following. First, creation of docker
container associated with the tool done with the script \CodeIn{install\_freefuzz\_docker.sh}. 
Then an example bug that is reproducible with the library version provided as an input is run as a sanity check. 
Then the preprocessing
script (\CodeIn{preprocess.py}) is executed to extract error types and buggy APIs for a specific library
vesion. Then the environment inside
the docker container of the tool is updated to match the library version passed as an input and the fuzzing tool runs inside the enviroment. After the execution is complete, the next step is running a postprocessing script (\CodeIn{postprocess.py}) that checks the execution log against the error types of the bug to determine if the bugs were reproduced or not.

For example, the following command runs FreeFuzz
on version 2.2.0 from \torch.

>>>>

\noindent
The script \CodeIn{install\_freefuzz\_docker.sh} build the docker
container that encapsulates FreeFuzz.

%% 
%% The script contains the following instructions:
%% % \Fix{add brief explanation for what it does}:
%% \begin{lstlisting}[language=bash,basicstyle=\small,keywords={}]
%% #!/bin/bash
%% git clone https://github.com/ise-uiuc/FreeFuzz.git
%% docker build -t freefuzz .
%% docker run --name freefuzz --gpus all -d freefuzz:latest
%% docker exec -it freefuzz mongorestore dump/
%% \end{lstlisting}

The following script runs FreeFuzz all bugs associated with version
2.2.0 of \torch.  The command \CodeIn{run-tool} takes the library
version as an input, along with the name of the docker container
(already created), the name of the library, and the user-provided
script containing the commands to run the tool
(\CodeIn{run\_freefuzz\_docker.sh}. The script reports on output how
many bugs are reproducible with this library version were successfully
reproduced by the given tool.  Tool execution proceeds as
follows. First, creation of docker container associated with the tool
done\Fix{ask gpt to revise/polish the text} with the script
\CodeIn{install\_freefuzz\_docker.sh}.  Then, an example bug\Fix{I
  don't understand ``example bug''. bugs in this version, no??!!} that
is reproducible with the library version provided as an input is run
as a sanity check.  Then, the preprocessing script
(\CodeIn{preprocess.py}) is executed to extract error types and buggy
APIs for a specific library vesion and the environment inside the
docker container of the tool is updated to match the library version
passed as an input and the fuzzing tool runs inside the
enviroment. After the execution is complete, the script finally runs a
postprocessing script (\CodeIn{postprocess.py}) to check the execution
log against the ground truth to determine if the bugs were reproduced
or not.
